\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Work on clients

@@

\end{pythoncode}
    \caption{Example of a simple \uwds filter, written in Python, and named {\tt
    walls\_filter}: the client connects to the \uwds network, walkthrough the
    scene graph of world {\tt example\_in}, filter out some objects, and publish
    the remaining objects in the world {\tt example\_out}.}

@@

\subsubsection{3D Visualization}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{uwds-screenshot}
    \caption{Screenshot of the {\tt uwds view} 3D visualization and manipulation
    tool.}
    \label{fig|uwds-view}
\end{figure}

@@

\subsubsection{Assets loading}

@@

{\tt uwds ls}
{\tt uwds show}

{\tt uwds explorer}

%%TODO add screenshot of uwds explorer

@@

@@

\subsection*{Architecture}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}

@@

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{uwds-screenshot}
    \caption{Screenshot of the {\tt uwds view} 3D visualization and manipulation
    tool. In this particular example, the 3D meshes have been pre-loaded using
    {\tt uwds load}. Their positions are then updated at run time using the
    robot's sensors and proprioception (joint state).}
    \label{fig|uwds-view}
\end{figure}

@@

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python, and named {\tt
    walls\_filter}: the client connects to the \uwds network, walkthrough the
    scene graph of world {\tt example\_in}, filter out some objects, and publish
    the remaining objects in the world {\tt example\_out}.}

@@

\subsubsection{3D Visualization and manipulation}

@@

@@

\paragraph{Assets loading}

@@

\uwds provides a range of tools to inspect a running the network. Graphical
tools ({\tt uwds explorer} and {\tt uwds timeline}, see Figure~\ref{fig|explorer})
provide an user-friendly overview of the system's graph with the connections
between the clients and the worlds as well as their activity.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{tools}
    \caption{Screenshots of the timeline (top) and network (bottom)
    introspection tools. Worlds are represented as boxes, clients as ellipses.}
    \label{fig|explorer}
\end{figure}

Specialized command-line tools are also available to list at run-time the worlds
and their content ({\tt uwds ls}) or to display detailed informations on a
specific node ({\tt uwds show}).

@@

\begin{listing}[h!]
\begin{pythoncode}
import copy
import underworlds
from underworlds.tools.visibility import VisibilityMonitor

with underworlds.Context("Human PoV") as ctx:

    source = ctx.worlds["base"]
    target = ctx.worlds["human_perspective"]

    # pick up the first node named 'human'
    human = source.scene.nodebyname("human")[0]
    target.scene.nodes.append(human)

    # VisibilityMonitor computes the set of visible 
    # nodes from a given viewpoint
    visibility = VisibilityMonitor(ctx, source)

    node_mapping = {}

        for node in visibility.from_camera(human):

            newnode = node.copy()

            # track the correspondence between nodes
            # in source and target scenes
            if node in node_mapping:
                newnode.id = node_mapping[node].id
            else:
                node_mapping[node] = newnode

            # reparent the nodes to the new root
            if node.parent == source.scene.rootnode.id:
                newnode.parent = target.scene.rootnode.id

            target.scene.nodes.update(newnode)

        source.scene.waitforchanges()

\end{pythoncode}
    \caption{This \uwds client creates a world named {\tt human\_perspective}
    from a source world {\tt base} by only updating objects that are in the
    human field of view. As such, {\tt human\_perspective} is a real-time model
    of the human perspective on the scene.}

    \label{lst|humanperspective} \end{listing}

@@

\subsection*{Architecture}
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}

@@

Representation of uncertainty

@@

Interplay with effort like RSG-DSL~\cite{blumenthal2014towards}
